flowCore a Bioconductor package for high throughput flow cytometry

### 2008-12-16 paper/bmc_article.tex
more changes
git-svn-id: https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/flowCore@35948 bc3139a8-67e5-0310-9ffc-ced21a209358

\subsection*{Standard flow operations}
Typically, the basic operations in FCM analyses adhere to the
following common work flow: the data need to be compensated (if that
was not already done on the instrument) and transformed, and
sub-populations of interest need to be selected based on a set of
(predominantly sequential) gates. All software solutions for FCM
analysis offer support for these operations, typically in an
interactive, GUI-driven interface. In \Rpackage{flowCore} we have
taken the approach to abstractly describe these operations and build a
set of tools to perform them on both \Rclass{flowFrames} and
\Rclass{flowSets}. While transformation, and to a certain extent
compensation, are fairly routine operations with only limited
potential for improvement, being able to implement new methodologies
for gating of FCM data, and extending the capabilities of
\Rpackage{flowCore} through object oriented programming are features
that clearly sets our framework apart from other FCM analysis
tools. By factoring out as much of the bookkeeping as possible,
programmers can focus on the actual operations rather then having to
deal with the tedious details of data integration and
access. Third-party methods can act on their own as first-class
citizens in the analysis framework, without breaking the work flow or
the basic infrastructure. This design allows for the straightforward
extension of \Rpackage{flowCore}'s capabilities, and has already
fostered the development of a number of valuable add-ons
\cite{lo2008agf,sarkar2008ufv}.

>>>>

\subsection*{Standard flow operations}
Typically, the basic operations in FCM analyses adhere to the
following common work flow: the data need to be compensated (if that
was not already done on the instrument) and transformed, and
sub-populations of interest need to be selected based on a set of
(predominantly sequential) gates. All software solutions for FCM
analysis offer support for these operations, typically in an
interactive, GUI-driven interface. In \Rpackage{flowCore} we have
taken the approach to abstractly describe these operations and build a
set of tools to perform them on both \Rclass{flowFrames} and
\Rclass{flowSets}. Typically, the results of these operations are
again \Rclass{flowFrame} or \Rclass{flwoSet} objects. While
transformation, and to a certain extent compensation, are fairly
routine operations with only limited potential for improvement, being
able to implement new methodologies for gating of FCM data, and
extending the capabilities of \Rpackage{flowCore} through object
oriented programming are features that clearly sets our framework
apart from other FCM analysis tools. By factoring out as much of the
bookkeeping as possible, programmers can focus on the actual
operations rather then having to deal with the tedious details of data
integration and access. Third-party methods can act on their own as
first-class citizens in the analysis framework, without breaking the
work flow or the basic infrastructure. This design allows for the
straightforward extension of \Rpackage{flowCore}'s capabilities, and
has already fostered the development of a number of valuable add-ons
\cite{lo2008agf,sarkar2008ufv}.
